Examining background gene lists in clusterProfiler - RNA-seq example

### 2024-05-31 analysis/analyse_rnaseq.Rmd
fix

par(mar=c(c(5.1, 10.1, 4.1, 2.1) ))
barplot(t(df),beside=TRUE,horiz=TRUE,las=1,
  xlab="no. significant sets", main="Comparison of original and corrected data",
  col=c("gray30","gray80"))

@@

signif(jac,3) %>%
  kbl(row.names = FALSE, caption="Jaccard similarity Corrected:Original") %>%
  kable_paper("hover", full_width = F)

>>>>

par(mar=c(c(5.1, 7.1, 4.1, 2.1) ))
barplot(t(df),beside=TRUE,horiz=TRUE,las=1,
  xlab="no. significant sets", main="Comparison of original and corrected data",
  col=c("gray30","gray80"))

@@

signif(jac,3) %>%
  kbl(row.names = TRUE, caption="Jaccard similarity Corrected:Original") %>%
  kable_paper("hover", full_width = F)
